Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/computation.tex
Working on 3

>>>>

As said in the introduction, any cell of $\mathcal{C}$ can be
characterized as a point with integer coordinates, aka \emph{lattice
point}. For instance, a standard way is to double the coordinates of
the centroid of the cell (often called its Khalimsky code). Now we
have to represent an arbitrary set $K$ of lattice points.

We may choose an arbitrary projection \emph{axis} $a \in
\{1,\ldots,d\}$. Letting $\pi_a$ be the projector along this axis, we
can collect all the cells of $K$ that projects onto the same
points. Let $p \in K$. Then $\pi^{-1}_a(p)$ is a set of cells having
all the same coordinates except along coordinate $a$. This set can be ordered increasingly
